### 2013-09-14 results.tex
fixed citations; more to be fixed
text surrounding the MR / ARFI volume figs
added axis data table
text additions for figures

\begin{itemize}
    \item Images of select cases, demonstrating segmentation process
    \item Table of volumes in MR and ARFI images
    \item Table comparing measurements
\end{itemize}

>>>>

\begin{itemize}
    \item Images of select cases, demonstrating segmentation process
\end{itemize}

The computed volumes of the prostates from the MR and ARFI imaging data are
presented in Table~\ref{tab:fig_mr_arfi_volumes}.  The subvolumes associated
with the zonal anatomy in each imaging modality was measured
(Figure~\ref{fig:fig_mr_arfi_volumes}(a)), showing an mean overestimation of
total prostate volume of 36.7 $\pm$ 27.9\% by ARFI imaging compared to MR
volumes (Figure~\ref{fig:fig_mr_arfi_volumes}(b)), and a relative
underestimation of the central zone volume relative to the central gland in MR
imaging of -15.3 $\pm$ 13.0 \% (Figure~\ref{fig:fig_mr_arfi_volumes}(c)).

\input{tab_mr_arfi_volumes}

\input{fig_mr_arfi_volumes}

MR and ARFI imaging total prostate volumes were also compared with the weights
and prostate volumes, approximated to be tri-axial ellipsoids, and calculated
from measurements of the prostate semi-principal axes.  That was no significant
correlation between the prostate weight and the image-reconstructed prostate
volumes (Figure~\ref{fig:fig_mr_arfi_weight}, R$^2$ = 0.05 (MR) and 0.13
(ARFI)), and there was XXXX correlation with the ellipsoidal approximation of
the measurement prostate volume and the image-recontructed volumens (Figure
XX).

\input{fig_mr_arfi_weight}

\input{tab_mr_arfi_axes}
